Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-05-07 ms.tex
more fix up of model description

The primary FDS99 analysis considered the grain properties, for example the
emissivity power law indices $\beta$, to be constant over the sky, and 
performed a correlation slope analysis to constrain these parameters with
FIRAS and DIRBE observations. A DIRBE 240$\mu$m/100$\mu$m ratio was constructed
to account for temperature variation at $\sim$1.3$^{\circ}$ resolution. In this
work we seek to apply FDS99-like emission models to the \PLANCK~data set, which
offers a dramatic enhancement in angular resolution relative to the FIRAS 
spectra. The \PLANCK~data allow us to derive a temperature correction at 
near-\IRAS~resolution, re-evaluate the best-fit global dust properties, and
fit additional parameters of the two-component model as a function of position
on the sky.

@@

Importantly, the emissivity power law indices $\beta$ of the two species 
differ.In accordance with the conventions of FDS99, $\nu_0$ is chosen to be 
3000 GHz. In principle, one could imagine this two MBB model to be specified by
seven free parameters for every line of sight: $T_1$, $T_2$, $\beta_1$, 
$\beta_2$, $f_1$, and $q_1$/$q_2$ and the normalization of $M_{\nu}$. However, 
as discussed in FDS99, $T_1$=$T_1$($T_2$, $\beta_1$, $\beta_2$, $q_1/q_2$) is 
fully specified by these other parameters under the assumption that the 
temperature of each species is determined by maintaining thermal equilibrium 
with the same ISRF. $T_1$ is always related to $T_2$ via a simple power law, 
although the prefactor and exponent depend on the parameters $q_1/q_2$, 
$\beta_1$ and $\beta_2$. $q_1/q_2$ encodes the relative emission/absorption 
cross-sections of the two dust species, while $f_1$ dictates the relative 
amounts of each species present.

>>>>

The primary FDS99 analysis considered the intrinsic grain properties, for 
example the emissivity power law indices, to be constant over the sky, and 
performed a correlation slope analysis to constrain these parameters with FIRAS
and DIRBE observations. FDS99 also constructed a DIRBE 240$\mu$m/100$\mu$m 
ratio to account for temperature variation at $\sim$1.3$^{\circ}$ resolution. 
In this work we seek to apply FDS99-like emission models to the \PLANCK~data 
set, which offers a dramatic enhancement in angular resolution relative to the 
FIRAS spectra. The \PLANCK~data thereby allow us to derive an improved 
temperature correction at near-\IRAS~resolution, re-evaluate the best-fit 
global dust properties, and fit additional parameters of the two-component 
model as a function of position on the sky.

% kind of feel like i'm re-writing the introduction here ??

@@

% re: following sentence --- in the code nu_0 is actually 2997.92458
% because this is the frequency with respect to which DIRBE color correction
% K_100 (and my color correction as well) is referenced

Following the convention of FDS99, $\nu_0$ is chosen to be 3000 GHz. In 
principle, one could imagine this two MBB model to be specified by seven free 
parameters for every line of sight: $T_1$, $T_2$, $\beta_1$, $\beta_2$, $f_1$, 
and $q_1$/$q_2$ and the normalization of $M_{\nu}$. However, as discussed in 
FDS99, $T_1$=$T_1$($T_2$, $\beta_1$, $\beta_2$, $q_1/q_2$) is fully specified 
by these other parameters under the assumption that the temperature of each 
species is determined by maintaining thermal equilibrium with the same ISRF. 
$T_1$ is always related to $T_2$ via a simple power law, although the prefactor
and exponent depend on the parameters $q_1/q_2$, $\beta_1$ and $\beta_2$. 
$q_1/q_2$ encodes the relative emission/absorption cross-sections of the two 
dust species, while $f_1$ dictates the relative amounts of each species 
present.

% Importantly, the emissivity power law indices $\beta$ of the two species 
% differ.
